### 2019-07-12 README.Rmd
Use gfm for README
This replaces markdown_github, which was deprecated
Add a note about updating `hurricaneexposuredata`

---
output:
  md_document:
    variant: markdown_github
---

@@

>>>>

---
output:
  md_document:
    variant: gfm
---

@@

You will want to have the latest version of the `hurricaneexposuredata` package. If you have previously installed `hurricaneexposuredata`, you may need to re-run the above code if you update the `hurricaneexposure` package, to update to the latest data.
